### 2024-11-19 Article/Background_sections/Adhesivity.tex
minima

\begin{definition}(Van Kampen property)
    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
    % \[
    % \begin{tikzcd}
    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
    %     C \arrow[r, "g" swap]                & D
    % \end{tikzcd}
    % \]
	\iffalse
    \[
    \begin{tikzcd}[row sep = scriptsize]
        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
        & C \arrow[r, "g" swap]                & D                  & \\
        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
    \end{tikzcd}
    \]
	\fi
    \[\begin{tikzcd}[row sep=25, column sep=25]
	& {A'} && {B'} \\
	{C'} && {D'} \\
	& A && B \\
	C && D
	\arrow["{f'}", from=1-2, to=1-4]
	\arrow["{m'}"', from=1-2, to=2-1]
	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n'}"', from=1-4, to=2-3]
	\arrow["b", from=1-4, to=3-4]
	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["c"', from=2-1, to=4-1]
	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
	\arrow["m", from=3-2, to=4-1]
	\arrow["n", from=3-4, to=4-3]
	\arrow["g"', from=4-1, to=4-3]
    \end{tikzcd}\]
    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
    \begin{itemize}
        \item it is a pushout;
        \item $a, b, c, d \in \mathcal{A}$;
%        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
	\item whenever the back and the left squares of the cube are pullbacks, then the top square is a pullback if and only if the front and the right squares are pullbacks.
    \end{itemize}
\end{definition}

@@

\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
    \begin{enumerate}
        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
    \end{enumerate}
    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive. \todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
\end{definition}

\begin{obs}
    $\Set$ is adhesive.
    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
\end{obs}

@@

\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback. \todo{almeno la seconda parte devi provarla o citarla per le M-adesive}
\end{prop}

@@

	We have then that the top face is a pullback, and by \Cref{prop:kermono}, the left face is a pullback. Since the bottom face is a pushout by hypothesis, we have that the front face and the right one are pullbacks (by adhesivity). Hence, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.
\end{proof}

@@

\color{blue}\todo{Ti inserisco una versione un po' più generale del lemma sotto}

\begin{lemma}\label{lemma:pushouts_kernel_pairs}
	Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube below the top face is an $\mathcal{M}$-pushout.
	\[\begin{tikzcd}[row sep=25, column sep=25]
		& {A'} && {B'} \\
		{C'} && {D'} \\
		& A && B \\
		C && D
		\arrow["{f'}", from=1-2, to=1-4]
		\arrow["{m'}"', from=1-2, to=2-1]
		\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
		\arrow["{n'}"', from=1-4, to=2-3]
		\arrow["b", from=1-4, to=3-4]
		\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
		\arrow["c"', from=2-1, to=4-1]
		\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
		\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
		\arrow["m", from=3-2, to=4-1]
		\arrow["n", from=3-4, to=4-3]
		\arrow["g"', from=4-1, to=4-3]
	\end{tikzcd}\]

@@

\begin{proof}
	Since $f'$, being the pullback of $f$, is in $\mathcal{M}$ then by  \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats} the bottom face of the cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks \todo{Nota che le frecce verticali NON sono mono in generale: qua serve adesività forte}.
	\[\begin{tikzcd}[row sep = 20, column sep = 20]
		& {K_a} && {K_b} \\
		{K_c} && {K_d} \\
		& {A'} && {B'} \\
		{C'} && {D'}
		\arrow["{k_{f'}}", from=1-2, to=1-4]
		\arrow["{k_{m'}}"', from=1-2, to=2-1]
		\arrow["{\pi_a^1}"{pos=0.7}, from=1-2, to=3-2]
		\arrow["{k_{n'}}", from=1-4, to=2-3]
		\arrow["{\pi_b^1}", from=1-4, to=3-4]
		\arrow["{k_{g'}}"{pos=0.7}, from=2-1, to=2-3, crossing over]
		\arrow["{\pi_c^1}"', from=2-1, to=4-1]
		\arrow["{f'}"'{pos=0.3}, from=3-2, to=3-4]
		\arrow["{\pi_d^1}"{pos=0.7}, from=2-3, to=4-3, crossing over]
		\arrow["{m'}", from=3-2, to=4-1]
		\arrow["{n'}", from=3-4, to=4-3]
		\arrow["{g'}"', from=4-1, to=4-3]
	\end{tikzcd}\]

@@

\color{black}

\begin{lemma}\label{lemma:pushouts_kernel_pairs}
    Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
        \[\begin{tikzcd}[row sep=25, column sep=25]
	& {A'} && {B'} \\
	{C'} && {D'} \\
	& A && B \\
	C && D
	\arrow["{f'}", from=1-2, to=1-4]
	\arrow["{m'}"', from=1-2, to=2-1]
	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n'}"', from=1-4, to=2-3]
	\arrow["b", from=1-4, to=3-4]
	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["c"', from=2-1, to=4-1]
	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
	\arrow["m", from=3-2, to=4-1]
	\arrow["n", from=3-4, to=4-3]
	\arrow["g"', from=4-1, to=4-3]
    \end{tikzcd}\]

>>>>

\begin{definition}(Van Kampen property)
    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
    % \[
    % \begin{tikzcd}
    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
    %     C \arrow[r, "g" swap]                & D
    % \end{tikzcd}
    % \]
	\iffalse
    \[
    \begin{tikzcd}[row sep = scriptsize]
        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
        & C \arrow[r, "g" swap]                & D                  & \\
        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
    \end{tikzcd}
    \]
	\fi
    \[\begin{tikzcd}[row sep=25, column sep=25]
	& {A'} && {B'} \\
	{C'} && {D'} \\
	& A && B \\
	C && D
	\arrow["{f'}", from=1-2, to=1-4]
	\arrow["{m'}"', from=1-2, to=2-1]
	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n'}"', from=1-4, to=2-3]
	\arrow["b", from=1-4, to=3-4]
	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["c"', from=2-1, to=4-1]
	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
	\arrow["m", from=3-2, to=4-1]
	\arrow["n", from=3-4, to=4-3]
	\arrow["g"', from=4-1, to=4-3]
    \end{tikzcd}\]
    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
    \begin{itemize}
        \item it is a pushout;
        \item $a, b, c, d \in \mathcal{A}$;
%        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
	\item whenever the back and the left squares of the cube are pullbacks, then the top square is a pullback if and only if the front and the right squares are pullbacks.
    \end{itemize}
	when in the last requirement holds only the \textit{if} part, we say that the category is $\mathcal{A}$-stable. Moreover, $\Hom(\cat C)$-Van Kampen squares are said to be \emph{Van Kampen}, and $\Hom(\cat C)$-stable squares are called \emph{stable}.
\end{definition}

@@

\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
    \begin{enumerate}
        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
    \end{enumerate}
	$\cat C$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen sqaures.
	We also say that $\cat C$ is \emph{adhesive} when it is strictly $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is strictly $\Reg(\cat C)$-adhesive.% \todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
\end{definition}

    %We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive. \todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
\begin{obs}
    $\Set$ is adhesive.
    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
\end{obs}

@@

\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback. %\todo{almeno la seconda parte devi provarla o citarla per le M-adesive}
	In $\mathcal{M}$-adhesive categories, $\mathcal{M}$-pushouts are pullbacks.
\end{prop}

@@

	We have then that the top face is a pullback, and by \Cref{prop:kermono}, the left face is a pullback. Since the bottom face is a pushout by hypothesis, we have that the front face and the right one are pullbacks (by adhesivity). Hence, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.

	Suppose now that $\cat C$ is $\mathcal{M}$-adhesive, and let the following square be a $\mathcal{M}$-pushout, so $m, n \in \mathcal{M}$.
	\[\begin{tikzcd}[row sep = 26, column sep = 26]
		A \ar[r, "f"] \ar[d, "m"swap] & B \ar[d, "n"] \\
		C \ar[r, "g"swap] & D
	\end{tikzcd}\]
	Consider now the following cube.
	\[\begin{tikzcd}[row sep = 20, column sep = 20]
	& A && B \\
	A && B \\
	& A && B \\
	C && D \\
	& {}
	\arrow["f", from=1-2, to=1-4]
	\arrow["{id_A}"', from=1-2, to=2-1]
	\arrow["{id_A}"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{id_B}"', from=1-4, to=2-3]
	\arrow["{id_B}", from=1-4, to=3-4]
	\arrow["m"', from=2-1, to=4-1]
	\arrow["f"{pos=0.7}, from=3-2, to=3-4]
	\arrow["m"', from=3-2, to=4-1]
	\arrow["n", from=3-4, to=4-3]
	\arrow["g"', from=4-1, to=4-3]
	\arrow["f"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["n"'{pos=0.7}, from=2-3, to=4-3, crossing over]
	\end{tikzcd}\]
	By the same argument as before, we can conclude that the starting square is a pullback.
\end{proof}

@@

\begin{lemma}\label{lemma:pushouts_kernel_pairs}
	Let $\cat C$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube below the top face is an $\mathcal{M}$-pushout.
	\[\begin{tikzcd}[row sep=25, column sep=25]
		& {A'} && {B'} \\
		{C'} && {D'} \\
		& A && B \\
		C && D
		\arrow["{f'}", from=1-2, to=1-4]
		\arrow["{m'}"', from=1-2, to=2-1]
		\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
		\arrow["{n'}"', from=1-4, to=2-3]
		\arrow["b", from=1-4, to=3-4]
		\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
		\arrow["c"', from=2-1, to=4-1]
		\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
		\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
		\arrow["m", from=3-2, to=4-1]
		\arrow["n", from=3-4, to=4-3]
		\arrow["g"', from=4-1, to=4-3]
	\end{tikzcd}\]

@@

\begin{proof}
	Since $f'$, being the pullback of $f$, is in $\mathcal{M}$ then by  \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats} the bottom face of the cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
	\[\begin{tikzcd}[row sep = 20, column sep = 20]
		& {K_a} && {K_b} \\
		{K_c} && {K_d} \\
		& {A'} && {B'} \\
		{C'} && {D'}
		\arrow["{k_{f'}}", from=1-2, to=1-4]
		\arrow["{k_{m'}}"', from=1-2, to=2-1]
		\arrow["{\pi_a^1}"{pos=0.7}, from=1-2, to=3-2]
		\arrow["{k_{n'}}", from=1-4, to=2-3]
		\arrow["{\pi_b^1}", from=1-4, to=3-4]
		\arrow["{k_{g'}}"{pos=0.7}, from=2-1, to=2-3, crossing over]
		\arrow["{\pi_c^1}"', from=2-1, to=4-1]
		\arrow["{f'}"'{pos=0.3}, from=3-2, to=3-4]
		\arrow["{\pi_d^1}"{pos=0.7}, from=2-3, to=4-3, crossing over]
		\arrow["{m'}", from=3-2, to=4-1]
		\arrow["{n'}", from=3-4, to=4-3]
		\arrow["{g'}"', from=4-1, to=4-3]
	\end{tikzcd}\]

@@

\begin{lemma}\label{lemma:pushouts_kernel_pairs}
    Let $\cat C$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
        \[\begin{tikzcd}[row sep=25, column sep=25]
	& {A'} && {B'} \\
	{C'} && {D'} \\
	& A && B \\
	C && D
	\arrow["{f'}", from=1-2, to=1-4]
	\arrow["{m'}"', from=1-2, to=2-1]
	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n'}"', from=1-4, to=2-3]
	\arrow["b", from=1-4, to=3-4]
	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["c"', from=2-1, to=4-1]
	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
	\arrow["m", from=3-2, to=4-1]
	\arrow["n", from=3-4, to=4-3]
	\arrow["g"', from=4-1, to=4-3]
    \end{tikzcd}\]

### 2024-11-19 Article/Graph_sections/EGGs.tex
minima

\begin{proof}
	Let $\eqgraph{G}_1 = (A_1, B_1, C_1, s_1, t_1, q_1)$, $\eqgraph{G}_2 = (A_2, B_2, C_2, s_2, t_2, q_2)$ and $\eqgraph{G}_3 = (A_3, B_3, C_3, s_3, t_3, q_3)$ be e-graphs,  $h: \eqgraph{G}_1 \to \eqgraph{G}_2$ and $m: \eqgraph{G}_1 \to \eqgraph{G}_3$ be two morphisms with $m$ mono. Let now $\eqgraph{P} = (A, B, C, s, t, q)$, together with $k: \eqgraph{G}_3 \to \eqgraph{P}$ and $n: \eqgraph{G}_2 \to \eqgraph{P}$, the pushout of $h$ and $m$.
	Let $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i\circ s_i$, for $i = 1, 2, 3$, and let $(U, u_1, u_2)$ be the kernel pair of $q \circ s$.
	Consider the following cube in $\Set$
	\[\begin{tikzcd}[row sep=25, column sep = 25]
	& {A_1} && {A_2} \\
	{A_3} && A \\
	& {C_1} && {C_2} \\
	{C_3} && C
	\arrow["{h_E}", from=1-2, to=1-4]
	\arrow["{m_E}"', from=1-2, to=2-1]
	\arrow["{q_1\circ s_1}"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n_E}", from=1-4, to=2-3]
	\arrow["{q_2\circ s_2}", from=1-4, to=3-4]
	\arrow["{k_E}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["{q_3\circ s_3}"', from=2-1, to=4-1]
	\arrow["{h_C}"{pos=0.8}, from=3-2, to=3-4]
	\arrow["{m_C}"', from=3-2, to=4-1]
	\arrow["{n_C}", from=3-4, to=4-3]
	\arrow["{k_C}"', from=4-1, to=4-3]
	\arrow["{q\circ s}"'{pos=0.2}, from=2-3, to=4-3, crossing over]
	\end{tikzcd}\]
	By adhesivity of $\Set$, and since $m$ is regular mono, the cube above is Van Kampen \todo{Non esisono i cubi di Van Kampen, a essere Van Kampen sono certi quadrati},

	\color{blue}

	Since $m$ is a regular mono then $m_C$ is mono by ???. Then, by adhesivity of $\Set$, the bottom face of the cube above is a Van Kampen square and thus a pullback. Therefore by \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout.
	\color{black}

	 and, by \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, all the \todo{vertical} faces are pullbacks. Then, applying \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout
	\[\begin{tikzcd}[row sep=27, column sep = 27]
		K_1 \ar[r, "{f_h}"] \ar[d, "{f_m}"swap] & K_2 \ar[d, "{f_n}"] \\
		K_3 \ar[r, "{f_k}"swap] & U
	\end{tikzcd}\]

@@

	Computing, we have
	\[
		\begin{split}
			q \circ t \circ u_1 \circ f_n &= q \circ t \circ n_E \circ \pi_2^1 \\ &= n_C \circ q_2 \circ s_2 \circ \pi_2^1 \\&= n_C \circ q_2 \circ s_2 \circ \pi_2^2 \\&=q \circ t \circ u_2 \circ f_n 
			\end{split}
			\qquad
			\begin{split} q \circ t \circ u_1 \circ f_k &= q \circ t \circ k_E \circ \pi_3^1 \\ &= k_C \circ q_3 \circ s_3 \circ \pi_3^1 \\&= k_C \circ q_3 \circ s_3 \circ \pi_3^2 \\&=q \circ t \circ u_2 \circ f_k
			\end{split}
	\]
	By universal property of pushouts, we can conclude $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis. \todo{Qua estendi un pochino: da questo si deduce che esiste una freccia blah blah}
\end{proof}

>>>>

\begin{proof}
	Let $\eqgraph{G}_1 = (A_1, B_1, C_1, s_1, t_1, q_1)$, $\eqgraph{G}_2 = (A_2, B_2, C_2, s_2, t_2, q_2)$ and $\eqgraph{G}_3 = (A_3, B_3, C_3, s_3, t_3, q_3)$ be e-graphs,  $h: \eqgraph{G}_1 \to \eqgraph{G}_2$ and $m: \eqgraph{G}_1 \to \eqgraph{G}_3$ be two morphisms with $m$ mono. Let now $\eqgraph{P} = (A, B, C, s, t, q)$, together with $k: \eqgraph{G}_3 \to \eqgraph{P}$ and $n: \eqgraph{G}_2 \to \eqgraph{P}$, the pushout of $h$ and $m$.
	Let $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i\circ s_i$, for $i = 1, 2, 3$, and let $(U, u_1, u_2)$ be the kernel pair of $q \circ s$.
	Consider the following cube in $\Set$
	\[\begin{tikzcd}[row sep=25, column sep = 25]
	& {A_1} && {A_2} \\
	{A_3} && A \\
	& {C_1} && {C_2} \\
	{C_3} && C
	\arrow["{h_E}", from=1-2, to=1-4]
	\arrow["{m_E}"', from=1-2, to=2-1]
	\arrow["{q_1\circ s_1}"'{pos=0.7}, from=1-2, to=3-2]
	\arrow["{n_E}", from=1-4, to=2-3]
	\arrow["{q_2\circ s_2}", from=1-4, to=3-4]
	\arrow["{k_E}"{pos=0.7}, from=2-1, to=2-3, crossing over]
	\arrow["{q_3\circ s_3}"', from=2-1, to=4-1]
	\arrow["{h_C}"{pos=0.8}, from=3-2, to=3-4]
	\arrow["{m_C}"', from=3-2, to=4-1]
	\arrow["{n_C}", from=3-4, to=4-3]
	\arrow["{k_C}"', from=4-1, to=4-3]
	\arrow["{q\circ s}"'{pos=0.2}, from=2-3, to=4-3, crossing over]
	\end{tikzcd}\]

	Since $m$ is a regular mono then $m_C$ is mono by \Cref{cor:reg_mono_EGG} and \Cref{cor:regmono}. Then, by adhesivity of $\Set$, the bottom face of the cube above is a Van Kampen square and thus a pullback. Therefore by \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout.

	\[\begin{tikzcd}[row sep=27, column sep = 27]
		K_1 \ar[r, "{f_h}"] \ar[d, "{f_m}"swap] & K_2 \ar[d, "{f_n}"] \\
		K_3 \ar[r, "{f_k}"swap] & U
	\end{tikzcd}\]

@@

	Computing, we have
	\[
		\begin{split}
			q \circ t \circ u_1 \circ f_n &= q \circ t \circ n_E \circ \pi_2^1 \\ &= n_C \circ q_2 \circ s_2 \circ \pi_2^1 \\&= n_C \circ q_2 \circ s_2 \circ \pi_2^2 \\&=q \circ t \circ u_2 \circ f_n 
			\end{split}
			\qquad
			\begin{split} q \circ t \circ u_1 \circ f_k &= q \circ t \circ k_E \circ \pi_3^1 \\ &= k_C \circ q_3 \circ s_3 \circ \pi_3^1 \\&= k_C \circ q_3 \circ s_3 \circ \pi_3^2 \\&=q \circ t \circ u_2 \circ f_k
			\end{split}
	\]
	By universal property of pushouts, there must exists a unque arrow $v: U \to C$ such that 
	\[\begin{split}v \circ f_n &= q \circ t \circ u_1 \circ f_n\\v\circ f_n  &= q \circ t \circ u_2 \circ f_n \end{split}\qquad\begin{split}v \circ f_k &= q \circ t \circ u_1 \circ f_k\\v \circ f_k &= q \circ t \circ u_2 \circ f_k\end{split}\]
		 hence, we deduce $q \circ t \circ u_1 = q \circ t \circ u_2$, and the thesis follows.
\end{proof}
